\LARGE \bf Towards a Data-driven Approach to Motion Planning

### 2015-02-27 paper2015asml.tex
adding note on why legibility is not important

We conducted an online survey\footnote{The online survey was conducted after gaining a waiver from SRI's IRB after a review of our survey procedure. Our survey followed standard guidelines for privacy of respondent information when conducting a survey on Mechanical Turk.} where we asked human observers to rate a variety of trajectories of the PR2 robot. \hl{Our intent with the survey was to get measures of how comfortable the observers were with the generated trajectories.} The survey was built on Amazon's Mechanical Turk, which has become a useful tool for large online data gathering and crowd-sourced work. Each respondent in the survey was presented with a set of demographic questions, a video, and asked to rate the robot's motion on the attributes  of elegance, efficiency, smoothness and overall impression (a summary of the rating scales used in the main survey question can be seen in Table~\ref{tab:rating_scales}). The ratings were later converted into numerical values on a scale of 1 to 7. Each respondent was expected to rate multiple trajectories but could not rate a trajectory more than once. Each video has four different views of the robot displayed simultaneously. Respondents were asked demographic questions about familiarity with video games, familiarity with robotics, age group and highest education level. The demographic information was not used to filter the responses we collected.

@@

\hl{We would also like to extend our set of features in multiple ways. We would like to include more dynamic features to capture the effect 
that the dynamics of the motions have on the perception of the motion. We would also like to introduce more environment specific features, e.g. the descriptors in}~\cite{10-jetchev-ICRA}, \hl{to account better for the effect of the environment on the ratings. Context and task specific features would be useful in capturing task specific motions, e.g. a robot turning a screwdriver may actually need to turn its wrist continuously. Incorporating task motions and relevant environments, e.g. picking up an object from a cluttered table, would also help in evaluating features like legibility. We would also like to examine how people's ratings change as they spend more time observing the robot (this effort will require a longer running survey or multiple surveys spaced apart in time). We would also like to include features to encode the choice of start and goal positions for the robot - several of the existing features could easily be adapated to take this into account.} The infrastructure that we have developed for generating and conducting 
surveys is fairly generic and could also easily be extended to surveying people using trajectories from real robots. This is another avenue we intend to explore 
in the near future. We also intend to explore the potential for open-sourcing the data and infrastructure to allow other researchers to conduct surveys of their own.

>>>>

We conducted an online survey\footnote{The online survey was conducted after gaining a waiver from SRI's IRB after a review of our survey procedure. Our survey followed standard guidelines for privacy of respondent information when conducting a survey on Mechanical Turk.} where we asked human observers to rate a variety of trajectories of the PR2 robot. \hl{Our intent with the survey was to get measures of how comfortable the observers were with the generated trajectories.} The survey was built on Amazon's Mechanical Turk, which has become a useful tool for large online data gathering and crowd-sourced work. Each respondent in the survey was presented with a set of demographic questions, a video, and asked to rate the robot's motion on the attributes  of elegance, efficiency, smoothness and overall impression (a summary of the rating scales used in the main survey question can be seen in Table~\ref{tab:rating_scales}). \hl{The users were shown the start and desired goal positions of the robot before they viewed the video of the motion. Thus, the users had prior information about the robot's intent.} The ratings were later converted into numerical values on a scale of 1 to 7. Each respondent was expected to rate multiple trajectories but could not rate a trajectory more than once. Each video has four different views of the robot displayed simultaneously. Respondents were asked demographic questions about familiarity with video games, familiarity with robotics, age group and highest education level. The demographic information was not used to filter the responses we collected.

@@

\hl{We would also like to extend our set of features in multiple ways. We would like to include more dynamic features to capture the effect 
that the dynamics of the motions have on the perception of the motion. We would also like to introduce more environment specific features, e.g. the descriptors in}~\cite{10-jetchev-ICRA}, \hl{to account better for the effect of the environment on the ratings. Context and task specific features would be useful in capturing task specific motions, e.g. a robot turning a screwdriver may actually need to turn its wrist continuously. Incorporating task motions and relevant environments, e.g. picking up an object from a cluttered table, would also help in evaluating features like legibility (note that legibility does not have a clear meaning in our experiments since the users already knew the robot's intent). We would also like to examine how people's ratings change as they spend more time observing the robot (this effort will require a longer running survey or multiple surveys spaced apart in time). We would also like to include features to encode the choice of start and goal positions for the robot - several of the existing features could easily be adapated to take this into account.} The infrastructure that we have developed for generating and conducting 
surveys is fairly generic and could also easily be extended to surveying people using trajectories from real robots. This is another avenue we intend to explore 
in the near future. We also intend to explore the potential for open-sourcing the data and infrastructure to allow other researchers to conduct surveys of their own.
